\bibitem{wordnet}
WordNet. --- \url{http://wordnet.princeton.edu/}

\bibitem{machinelearning}
Профессиональный информационно-аналитический ресурс, посвященный
машинному обучению, распознаванию образов и интеллектуальному анализу данных.--- \url{http://machinelearning.ru/}

\bibitem{graph_mashable}
Google knowledge graph. ---\url{http://mashable.com/2012/02/13/google-knowledge-graph-change-search/}

\bibitem{jwnl}
Java WordNet Library. ---\url{http://sourceforge.net/projects/jwordnet/}

\bibitem{strategy}
Starategy pattern. --- \url{http://en.wikipedia.org/wiki/Strategy_pattern}

\bibitem{text_mining_survey}
Hotho A. ~ 
A Brief Survey of Text Mining /
A.~Hotho, A.~Nurnberger, G.~Paass //  
LDV Forum --- GLDV Journal for Computational Linguistics
 and Language Technology. --- 2005. --- Vol.~ 20, № ~1 - P.~19-62.


\bibitem{thesaurus}
Nakayama~K.~Wikipedia mining for an association web thesaurus construction /
K.~Nakayama, T.~Hara , S.~Nishio // WISE. --- 2007. --- Springer. --- P.~322-334.
 
\bibitem{weka}
Hall~M.~The WEKA data mining software: an update /
 M.~Hall, E.~Frank, G.~Holmes, B.~Pfahringer, P.~Reutemann, I.~H.~Witten // 
 ACM SIGKDD Explorations Newsletter. --- 2009. --- Vol.~11, Issue~1. --- P.~10-18 
 
 \bibitem{knowledge_graph}
Zhang~L. ~  Knowledge graph theory and structural parsing //
 Twente University Press. --- 2002. ---  P.~216

 
\bibitem{complexSim}
Dingjia~L. ~
A Dependency Grammar and WordNet Based Sentence Similarity Measure /
Dingjia~LIU, Zequan LIU, Qian DONG //
Journal of Computational Information Systems. --- 2012. ---
Vol.~8, №~3. --- P.~1027-1035.
 
\bibitem{inproceedings}
WU~Z. ~
Verbs semantics and lexical selection /
 Z. WU, M. Palmer//
 Proceedings of the 32nd annual meeting on Association
for Computational Linguistics. --- 1994. --- P. 133--138
