\bibitem{wikipedia}
Wikipedia, the free encyclopedia. --- \url{http://www.wikipedia.org/}

\bibitem{download}
Wikipedia:Database download. --- \url{http://en.wikipedia.org/wiki/Wikipedia:Database_download}

\bibitem{schema}
Wikipedia's dumps XML Schema description. --- \url{http://www.mediawiki.org/xml/export-0.5.xsd}

\bibitem{dom}
Document Object Model, Wikipedia. --- \url{http://ru.wikipedia.org/wiki/Document_Object_Model}

\bibitem{sax}
Simple API for XML, Wikipedia. --- \url{http://ru.wikipedia.org/wiki/SAX}

\bibitem{callback}
Callback, Wikipedia. --- \url{http://ru.wikipedia.org/wiki/Callback}

\bibitem{wikimarkup}
Help:Wiki markup. --- \url{http://en.wikipedia.org/wiki/Help:Wiki_markup}

\bibitem{jwpl}
Java-based Wikipedia Library~
--- An application programming interface for Wikipedia \\
Google Project Hosting. --- \url{http://code.google.com/p/jwpl/}

\bibitem{mysql}
MySQL. --- \url{http://www.mysql.com}

\bibitem{lucene}
Apache Lucene Core. --- \url{http://lucene.apache.org/core/}

\bibitem{mongodb}
MongoDB. --- \url{http://www.mongodb.org/}

\bibitem{patternMapper}
Data Mapper, Martin Fowler. --- \url{http://martinfowler.com/eaaCatalog/dataMapper.html}

\bibitem{patternGateway}
Gateway, Martin Fowler. --- \url{http://martinfowler.com/eaaCatalog/gateway.html}

\bibitem{textminingsurvey}
Hotho~A.
A brief survey of text mining /
Andreas Hotho and Andreas Nürnberger and Gerhard Paaß //
LDV Forum - GLDV Journal for Computational Linguistics and Language Technology (2005)

\bibitem{corenlp}
Stanford CoreNLP, ~
The Stanford Natural Language Processing Group. ---
\url{http://nlp.stanford.edu/software/corenlp.shtml}

\bibitem{treebank}
Mitchell~P.~Marcus,~
Building a Large Annotated Corpus of English: The Penn Treebank /
Mitchell~P.~Marcus, Mary~Ann~Marcinkiewicz, Beatrice~Santorinit // 
Computational Linguistics 
Volume:~19, Number:~2 (1993).

\bibitem{homsky}
Chomsky,~N.~
Syntactic Structures./
Noal Chomsky //
1957. The~Hague/Paris:~Mouton.

\bibitem{dependencies}
M.C.~de~Marneffe,~
Stanford typed dependencies manual /
Marie-Catherine de Marneffe and Christopher D. Manning //
September 2008.

\bibitem{statisticalSim}
Zhang~J.~
Calculating Statistical Similarity between Sentences /
Junsheng Zhang, Yunchuan Sun, Huilin Wang, Yanqing He //
Journal of Convergence Information Technology,
Volume:~6, Number:~2. February 2011.

\bibitem{wordnetSim}
Dao,~T.N.~
Measuring Similarity between sentences /
Dao,~T.N. and Simpson,~T.//
Proceedings of the Document Understanding Conference. (2002)

\bibitem{hungarian}
Kuhn,~H.W.~
The Hungarian Method for the assignment problem /
Harold W. Kuhn // 
Naval Research Logistics Quarterly,
Volume:~2, P.~83—97, (1955).

\bibitem{weightedDep}
Lintean M.C.~
Paraphrase Identification Using Weighted Dependencies and Word Semantics./
Mihai~C.~Lintean, Vasile~Rus//
Informatica (Slovenia),
Volume:~34, Number:~1, P.~19-28 (2010).

\bibitem{complexSim}
Dingjia~LIU,~
A Dependency Grammar and WordNet Based Sentence Similarity Measure /
Dingjia~LIU, Zequan LIU, Qian DONG //
Journal of Computational Information Systems, 
Volume:~8, Number:~3, P.1027–1035 (2012).

\bibitem{wordnet}
Wordnet, A lexical database for English. ---
\url{http://wordnet.princeton.edu/}

\bibitem{github}
Academic TEXt ANalizing Tool, GitHub. ---~
\url{https://github.com/Atexant/atexant}
